---
title: B3 - Stock returns - ongoing project
author: Davi Simon
date: '2018-08-01'
slug: b3-stock-returns-ongoing-project
categories:
  - Finance
  - R
tags:
  - tidyquant
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r, echo=FALSE, message=FALSE, include=FALSE}
library(GetDFPData)
library(tidyquant)
library(dplyr)
library(readxl)
library(writexl)
library(stringr)
library(tidyverse)
library(rstudioapi)
library(magrittr)
library(tidyverse)
library(ggplot2)
library(dslabs)
library(lubridate)
require(zoo)
library(BatchGetSymbols)
require(xfun)
xfun::pkg_load2(c('base64enc', 'htmltools', 'mime'))

library(knitr)
library(kableExtra)

```



We start by defining which tickers are we going to consider in our analysis. The file "tickers.xlsx" has tickers from B3 stocks that were active in the stock exchange as of april 2018.


```{r echo=FALSE}
# a single file
xfun::embed_file('tickers.xlsx')
```

We will read it with the function read_excel, from the amazing readxl package <https://readxl.tidyverse.org/>

```{r readxl, eval=FALSE}
library(readxl)
```

Brazilian stocks are found in *yahoofinance* with an added ".SA". So, we add that suffix to the tickers, creating the codigo  column in our *tickers* dataframe. 

```{r tickers}
tickers <- read_excel("tickers.xlsx", sheet=1, col_names = TRUE)
tickers$codigo <- paste(tickers$`unique(Dados$Codigo)`,".SA",sep="")
lista <- tickers$codigo
```


Through tidyquant's *tq_get* function <https://cran.r-project.org/web/packages/tidyquant/index.html>, we get daily stock prices from <https://finance.yahoo.com/>, for all of our tickers. This may take a while, depending on the quality of your internet connection. 
In the same block of code, we transform daily prices on adjusted daily log returns.
Log returns are defined as follows: 

$$LogReturns = \log(\frac{P_{t}}{P_{t-1}})$$


```{r tidydplyr, eval=FALSE}
library(tidyquant)
library(dplyr)
```


```{r retornos diarios, eval=FALSE}
log_Retornos_diarios <-   lista %>%
  tq_get(get  = "stock.prices",
         from = "2001-01-01",
         to   = "2018-07-31") %>%
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily",
               type = "log",
               col_rename = "Ra")
```

```{r retornos1 diarios, echo=FALSE}
suppressWarnings( log_Retornos_diarios <-   lista %>%
  tq_get(get  = "stock.prices",
         from = "2001-01-01",
         to   = "2018-07-31") %>%
  group_by(symbol) %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily",
               type = "log",
               col_rename = "Ra"))
```


Next we get BOVESPA daily log returns, with a similar approach.

```{r retornos bolsa, eval=FALSE}
log_Rb <- "^BVSP" %>%
  tq_get(get  = "stock.prices",
         from = "2001-01-01",
         to   = "2018-07-31") %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily",
               type = "log",
               col_rename = "Rb")
```

```{r retornos1 bolsa, echo=FALSE}
 suppressWarnings( log_Rb <- "^BVSP" %>%
  tq_get(get  = "stock.prices",
         from = "2001-01-01",
         to   = "2018-07-31") %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               period     = "daily",
               type = "log",
               col_rename = "Rb") )
```


Now, considering that some of the possible uses of this dataset are dependent on calculating beta coefficients between the stocks and the index, we add a column containing daily log returns of the index to the object containing daily stock returns. We do that through dplyr::left_join function

```{r logretornos}
log_Retornos_diarios_indice <- left_join(log_Retornos_diarios, log_Rb, by = c("date" = "date"))
```

A basic inspection of the data:
```{r inspect}
head(log_Retornos_diarios_indice)
```

A few key statistics, per asset: 
```{r keystats}
log_Retornos_diarios_indice  %>% 
      group_by(symbol) %>% 
      summarise(mean = mean(Ra),
                sd = sd(Ra))
```


Key statistics with a much nicer presentation, per asset: 
```{r keystats1}
log_Retornos_diarios_indice  %>% 
      group_by(symbol) %>% 
      summarise(mean = mean(Ra),
                sd = sd(Ra))%>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover")) %>% 
  scroll_box(width = "100%", height = "200px")
```



Since it took a while to get data from the web, why not saving our resulting object? 
```{r saveRDS}
saveRDS(log_Retornos_diarios_indice, "log_Retornos_diarios_indice.rds")
```

This way you can open it later through: 
```{r readRDS}
log_Retornos_diarios_indice <-  readRDS("log_Retornos_diarios_indice.rds")
```

What's next? We'll get to it in a little while. 

