---
title: "My first post"
author: "Davi Souza Simon"
date: 2018-07-24T12:56:14-05:00
categories: ["R","Finance","Accounting"]
tags: ["R Markdown", "About"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r, echo=FALSE, message=FALSE, include=FALSE}

library(tidyquant)
library(dplyr)
library(readxl)
library(writexl)
library(stringr)
library(tidyverse)
library(rstudioapi)
library(magrittr)
library(tidyverse)
library(ggplot2)
library(dslabs)
library(lubridate)
```

# First post

First things first. 

1. Why having a website? I have a lot of code and ideas to share. 
2. Why now? Had to start it at some point. 
3. What will I blog about? Accounting, Corporate Finance, Governance (Public and Corporate), Pension Funds. R programming Language, Stata, Rmarkdown. Some others things will show up, I suppose. 
4. Will I update it frequently? Highly likely. 
5. How did I do it? <https://bookdown.org/yihui/blogdown/>
6. How long did it take? A couple of hours to get it up and running.

My posts will have code and reproducible examples like this. 

Getting Petrobras' stock data from <https://finance.yahoo.com/> with the tidyquant package <https://cran.r-project.org/web/packages/tidyquant/index.html>

```{r Petro}
Ra <- "PETR4.SA" %>%
  tq_get(get  = "stock.prices",
         from = "2015-07-21",
         to   = "2018-07-20") %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn,
               type       = "log",
               period     = "daily", 
               col_rename = "Ra")
```

Getting Ibovespa's returns in the same three year window. 
```{r Bolsa}
Rb <- "^BVSP" %>%
  tq_get(get  = "stock.prices",
         from = "2015-07-21",
         to   = "2018-07-20") %>%
  tq_transmute(select     = adjusted, 
               mutate_fun = periodReturn, 
               type       = "log",
               period     = "daily", 
               col_rename = "Rb")
```

Merging tables.
```{r Juntando}
RaRb <- left_join(Ra, Rb, by = c("date" = "date"))
```

Analyzing the variables.
```{r Juntando2}
summary(RaRb) 
```

Getting rid of missing data
```{r Juntando3}
RaRb <- RaRb %>% filter(!is.na(Rb))
```


## Will I post cool graphs?

You bet!
```{r Beta, tidy=FALSE}

ggplot(data=RaRb) + geom_point(aes(x=Rb, y=Ra)) + geom_smooth(aes(x=Rb, y=Ra), method="lm") + xlab("IBOVESPA") + ylab("PETR4") + 
  ggtitle("Beta from daily returns - 3 years from July 20, 2018)", subtitle = paste("R(PETR4) = Rf + ",round(coef(summary(lm(Ra~Rb, data=RaRb)))[2,1],2),"(Rm - Rf)",sep="")) + geom_vline(xintercept=0, color = "black") + geom_hline(yintercept=0, color = "black") 

```





